### 2016-10-25 paper/intro.tex
pass on text

Optimizing regression testing is important.  As software evolves the
size of test sets increases, potentially leading to disruption in the
development process caused by late reports of test failures.  This
problem manifests more dramatically at large IT companies
(e.g.,\Comment{ Groupon~\Fix{cite},} Google~\Fix{cite} and
Microsoft~\Fix{cite}) where the size of test sets often exceeds the
size of the code base.  Several approaches have been proposed to
optimize regression testing.  Research has focused mostly on test
selection~\Fix{cite}, test reduction~\Fix{cite}, and test
prioritization~\Fix{cite}.  Although these approaches can also be
applied in industrial settings, the focus in industry has been mostly
in parallelizing execution of tests using server farms,\Jbc{Is this an
assumption? Is there any evidence?} where worker machines from the
farm are assigned to execute distinct subsets of the original test
suite.

@@

%%  LocalWords:  parallelization multicore JUnit TestNG NUnit XXm YYm
%%  LocalWords:  Groupon parallelizing multi JVMs CPUs JVM

>>>>

As software evolves it is expected that the number of tests and the
length of test runs increase.  Both elements can add up on the
aggregate cost of running a test suite, leading to late reports of test
failures, which can disrupt the development
process~\cite{hilton-etal-ase2016}.  This is often referred to as the
``regression testing problem''.  At large IT companies (e.g.,
Groupon~\cite{kim-etal-fse2013}), dealing with high testing costs is a
common problem .  \Mar{Ask Milos if he can share stories on how
  prevalent regression testing is at Microsoft and Google, if he can
  explain how they run tests, and how prevalent is parallelization (in
  contrast to regression testing).}

Several approaches have been proposed in the literature to optimize
regression testing.  Research has focused mostly on test suite
minimization, prioritization, reduction, and
selection~\cite{yoo-harman-stvr2012}.  Most of these techniques are
unsound (\ie{}, they do not guarantee that failure-revealing tests
will be selected), however, more recently, sound techniques have been
proposed~\cite{gligoric-etal-issta2015,soetens-etal-2016}.  For
example, to obtain soundness,
Ekstazi\cite{ekstazi-web,gligoric-etal-issta2015} runs a change-impact
test analysis based on file dependencies computed and maintained at
low cost.

Although regression testing is a recognized problem in academia and at
large IT organizations, to the best of our knowledge no prior work has
investigated how prevalent the problem is in open-source projects.  We
assume that the alternative of renting server farms (or even building
one) to mitigate the problem is economically tempting for large IT
organizations but not so for open-source projects and projects of
smaller organizations with lower budgets for building a testing
infrastructure.  As such, this paper studies (1) how relevant the
problem of long-running test suites in open-source software really is,
(2) what are the causes of high execution costs (\eg{}, IO or CPU),
and (3) what is the impact of existing open-source sound approaches to
reducing cost.

\Fix{--------------}

@@

%%  LocalWords:  parallelization multicore JUnit TestNG NUnit XXm YYm
%%  LocalWords:  Groupon parallelizing multi JVMs CPUs JVM Milos TODO
%%  LocalWords:  Ekstazi
